### 2023-11-16 Codes/3_make_figures_publication.rmd
Updates from Overleaf
xiaofei's edut

```{r}
results <-
  here("Shared/Results/gaussian/pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))]
```

# The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T

```{r}
# fig.id = "pi-dif-dist",
# fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
mean_data_value <-
  results %>%
  .[, .(pi_diff = median(pi_diff)),
    by = c("field_col", "pLabel", "type")
  ]

# saveRDS(mean_data_value, "Shared/Results/mean_data_value.rds")

g_value <-
  results %>%
  ggplot(data = .) +
  geom_histogram(
    aes(x = pi_diff),
    fill = NA,
    color = "blue",
    bins = 50,
    linewidth = 0.2
  ) +
  geom_vline(
    data = mean_data_value,
    aes(xintercept = pi_diff),
    color = "red",
    linewidth = 0.5
  ) +
  geom_text(
    data = mean_data_value, color = "red",
    aes(
      x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20), y = 150,
      label = paste0("Median = ", round(pi_diff, 2))
    ),
    angle = 0,
    hjust = -0.1,
    vjust = 0,
    size = 3,
    family = "Times"
  ) +
  facet_grid(pLabel ~ type) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
  xlab("The value of VRA over URA ($ per ha)") +
  ylab("Number of Simulation Cases") +
  theme_fig

ggsave(
  "GitControlled/Writing/Figures/g_value.png",
  g_value,
  width = 6,
  height = 5,
  dpi = 600
)
```

# EONR estimation tendency

```{r}
# ggplot(est_data) +
# geom_histogram(aes(x = opt_N_scam)) +
# facet_grid(round(pN, digits = 2) ~ .)

est_data <-
  readRDS(here("Shared/Results/Gaussian/est_data.rds")) %>%
  unnest() %>%
  data.table() %>%
  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")]

eorn_ratio_data <-
  est_data %>%
  .[, pRatio := pN / pCorn] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))] %>%
  .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(type, sim, pLabel)]

g_eonr_bias <-
  ggplot(data = eorn_ratio_data) +
  geom_histogram(
    aes(x = eonr_ratio),
    color = "blue",
    fill = NA,
    bins = 50,
    size = 0.2
  ) +
  geom_vline(xintercept = 1, color = "red") +
  facet_grid(pLabel ~ type) +
  ylab("Number of Simulation Cases") +
  xlab("Average Ratio of Estimated EONR to true EONR") +
  theme_fig

@@

# Bias in the estimation of the value of GWR-based VRA over SCAM-based URA

```{r}
# fig.id = "bias-est-pi",
# fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"

# mean_data_bias[type == "GWRT" & pLabel == 10.35, bias] %>% hist

median_bias_data <-
  results %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  .[, .(bias = median(bias)),
    by = c("field_col", "pLabel", "type")
  ] %>%
  print()

g_bias <-
  results %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  .[bias < 150, ] %>%
  ggplot(data = .) +
  geom_histogram(
    aes(x = bias),
    fill = NA,
    color = "blue",
    size = 0.2,
    bins = 50
  ) +
  geom_vline(
    data = median_bias_data, aes(xintercept = bias),
    color = "red",
    size = 0.5
  ) +
  geom_text(
    data = median_bias_data, color = "red",
    aes(
      x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
      label = paste0("Median = ", round(bias, 2)),
      family = "Times"
    ),
    angle = 0, hjust = -0.1, vjust = 0, size = 3
  ) +
  facet_grid(pLabel ~ type) +
  scale_y_continuous(expand = c(0, 0)) +
  xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
  ylab("Number of Simulation Cases") +
  theme_fig

ggsave(
  "GitControlled/Writing/Figures/g_bias.png",
  g_bias,
  width = 6,
  height = 5,
  dpi = 600
)
```

>>>>

```{r}
results <-
  here("Shared/Results/gaussian/pi_data.rds") %>%
  readRDS() %>%
    # === do not need QD result
    .[model!="QD", ] %>% 
    # === modify model names
    .[model=="GWR-R", model := "GWRR"] %>% 
    .[model=="GWR-T", model := "GWRT"] %>% 
    # === only need  25% (5.44), 50% (6.56), 75% (7.67) price ratio
    .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
    # === label prices
    .[pRatio == 5.44, pLabel := "5.44 (Low)"] %>%
    .[pRatio == 6.56, pLabel := "6.56 (Middle)"] %>%
    .[pRatio == 7.67, pLabel := "7.67 (High)"] %>%
    # === estimation bias
    .[, bias := pi_diff_est - pi_diff]
```

# The value of GWR-based VRA over SCAM-based URA

```{r}
# fig.id = "value-vra",
# fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA"
mean_data_value <-
    results %>%
    .[, .(pi_diff = median(pi_diff),
          pi_diff_est = median(pi_diff_est),
          bias = median(bias)),
      by = c("field_col", "pLabel", "model")
    ]

g_value <-
  results %>%
  ggplot(data = .) +
  geom_histogram(
        aes(x = pi_diff, fill = "True", color = "True"),
        alpha = 0.1, bins = 80, size = 0.2
    ) +
    geom_histogram(
        aes(x = pi_diff_est, fill = "Estimated", color = "Estimated"),
        alpha = 0.4, bins = 80, size = 0.2
    ) +
    geom_vline(
        data = mean_data_value,
        aes(xintercept = pi_diff),
        color = "blue", size = 0.5
    ) +
    geom_vline(
        data = mean_data_value,
        aes(xintercept = pi_diff_est),
        color = "red", size = 0.5
    ) +
    geom_text(
        data = mean_data_value, color = "blue",
        aes(
            x = ifelse(pi_diff < 65, pi_diff - 5, pi_diff - 20), y = 100,
            label = paste0("Median=", round(pi_diff, 2))
        ),
        angle = 0, hjust = 0.9, vjust = 0, size = 2.5
    ) +
    geom_text(
        data = mean_data_value, color = "red",
        aes(
            x = ifelse(pi_diff_est < 65, pi_diff_est + 4, pi_diff_est - 20), y = 100,
            label = paste0("Median=", round(pi_diff_est, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 2.5
    ) +
    scale_color_manual(name = "", values = c("True" = "blue", "Estimated" = "red"),
                       breaks = c("True", "Estimated")) +
    scale_fill_manual(name = "", values = c("True" = "blue", "Estimated" = "red"),
                      breaks = c("True", "Estimated")) +
    facet_grid(pLabel ~ model) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(breaks = 20 * (-2:4), limits = c(-30, 90)) +
    scale_y_continuous(sec.axis = sec_axis(~ . , name = "Nitrogen-Corn Price Ratio", breaks = NULL, labels = NULL),
                       expand = c(0, 0)) +
    xlab("Economic value of VRA over URA ($ per ha)") +
    ylab("Number of Simulation Cases") +
    theme(
        text = element_text(family = "Times New Roman"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA),
        legend.position='bottom',
        legend.key.size = unit(0.3, 'cm')
    ) +
  theme_fig

ggsave(
  "GitControlled/Writing/Figures/g_value.png",
  g_value,
  width = 7,
  height = 5,
  dpi = 600
)
```

# EONR estimation bias

```{r}
est_data <-
  readRDS(here("Shared/Results/Gaussian/est_data.rds")) %>%
  unnest() %>%
  data.table()

eorn_ratio_data <-
  est_data %>%
  .[, pRatio := pN / pCorn] %>%
    # === do not need QD result
    .[model!="QD", ] %>% 
    # === modify model names
    .[model=="GWR-R", model := "GWRR"] %>% 
    .[model=="GWR-T", model := "GWRT"] %>% 
    # === only need  25% (5.44), 50% (6.56), 75% (7.67) price ratio
    .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
    # === label prices
    .[pRatio == 5.44, pLabel := "5.44 (Low)"] %>%
    .[pRatio == 6.56, pLabel := "6.56 (Middle)"] %>%
    .[pRatio == 7.67, pLabel := "7.67 (High)"] %>% 
    .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(model, sim, pLabel)]

g_eonr_bias <-
  ggplot(data = eorn_ratio_data) +
  geom_histogram(
    aes(x = eonr_ratio),
    color = "black",
    fill = NA,
    bins = 50,
    size = 0.2
  ) +
  geom_vline(xintercept = 1, color = "black") +
  facet_grid(pLabel ~ model) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "Nitrogen-Corn Price Ratio", breaks = NULL, labels = NULL),
                       expand = c(0, 0)) +
  ylab("Number of Simulation Cases") +
  xlab("Average Ratio of Estimated EONR to true EONR") +
  theme_fig

@@
